My title

### 2024-11-28 paper/paper.qmd
finished model construction

### Model justification

@@

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

@@

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

>>>>

\[
Population_{it} = \beta_0 + \beta_1 \cdot cd\_occupied_t + \beta_2 \cdot french\_surrender_t + \beta_3 \cdot is\_occupied_t + \beta_4 \cdot DistrictType_i + \beta_5 \cdot (cd\_occupied_t \times DistrictType_i) + \beta_6 \cdot (french\_surrender_t \times DistrictType_i) + \beta_7\cdot (is\_occupied_t \times DistrictType_i) + \epsilon{it}
\]
### Model justification

@@

did_model <-
  readRDS(file = here::here("models/did_model.rds"))
```

@@

modelsummary::modelsummary(
  list(
    "Population model" = did_model
  ),
  statistic = "mad",
  fmt = 2
)
```
